Copy and paste the following to the gray box to install the more common packages. To run code, you can either click "CTRL + Enter" or choose "Run in the top corner"  

  install.packages("ggplot2")
  library(ggplot2)
  install.packages("tidyr")
  library(tidyr)
  install.packages("dplyr")
  library(dplyr)
  install.packages("tidyverse")
  library(tidyverse)
  install.packages("Basics")
  library(Basics)
  
``` {r, Install packages}

  install.packages("ggplot2")
  library(ggplot2)
  install.packages("tidyr")
  library(tidyr)
  install.packages("dplyr")
  library(dplyr)
  install.packages("tidyverse")
  library(tidyverse)
  install.packages("Basics")
  library(Basics)
```
  
You now have the basic packages installed- learn more about these packages by running function

Step 1 will give more information regarding the package
Step 2 will give you an example and result of what happens when running the code



Step 1: copy and paste function to the below box: ggplot2Basics()

Step 2: copy and paste function to the below box: 
  ggplot(mtcars, aes(x=hp, y=mpg)) +
    geom_point()
    

Step 3: change the graph from a dot graph to a line graph by replacing
"geom_point" with "geom_line". 


``` {r, ggplot2Basics}


  
```

Step 1: copy and paste function to the below box: tidyrBasics()

Step 2: copy and paste function to the below box to see what they do: 
mtcars %>% gather(mpg, hp)
mtcars %>% separate()
mtcars %>% spread()


``` {r, tidyrBasics}

  
```

Step 1: copy and paste function to the below box: dplyrBasics()

Step 2: copy and paste function to the below box to see what they do: 
mtcars %>% mutate(mph,wt/hp)
mtcars %>% rownames_to_column() %>%
select(rowname, "^M")
mtcars %>% filter(mph= 21)
mtcars %>% summarize(mean=mean(wt))
mtcars %>% arrange(desc(wt))



``` {r, dplyrBasics}



  
```
